% !TEX program = xelatex
% Resume by ice1000

\documentclass{resume}

\usepackage{linespacing_fix} % Disable extra space before next section
\usepackage{geometry}
\geometry{a4paper, left=1.5cm, right=1.5cm, top=0.9cm, bottom=0.7cm}
\usepackage{hyperref} % For hyperlinks

\begin{document}

\name{ZIQI XIE}

\basicInfo{\textperiodcentered\
  \email{zxstardfw@gmail.com} \textperiodcentered\
  \phone{(+1) 617-820-2833}
}

\section{Education}
\datedsubsection{\textbf{Tulane University}, New Orleans, LA}{07/2015 -- 05/2020}
\textbf{Ph.D. Economics (STEM)}  
Research Interests: Applied Microeconomics, Corporate Finance, Causal Inference
%\datedsubsection{\textbf{Northeastern University}, Boston, MA}{09/2012 -- 05/2014}
%\textbf{M.A. Economics}  


\section{Experience}

%\datedsubsection{\textbf{Modal Learning}}{10/2023 -- Present}
%\textbf{Data Advisory Board Member}  
%\begin{itemize}
    %\item Provide industry-leading advisory to Modal, an online learning startup, focusing on product development and data strategy.
%\end{itemize}

\datedsubsection{\textbf{Comerica Bank}}{09/2020 -- Present}
\textbf{Vice President, Credit Analytics and Strategy}\\
\textbf{Social Impact Committee Chair (Comerica Asian/Pacific Islander Group)}
\begin{itemize}
    \item \textbf{Leadership Development Program (Selective Cohort)}  
    \begin{itemize}
        \item Selected as one of a small, highly competitive cohort for the bank’s enterprise leadership development program. Conceived and led a \$5MM strategic vision initiative to redesign the bank’s digital application ecosystem by integrating customer-need segmentation, behavioral analytics, and cross-sell optimization logic.
        \item Built a business case covering ROI, customer acquisition uplift, and risk governance, and presented recommendations to the Executive Management Committee and C-suite, influencing long-term digital and product strategy.
    \end{itemize}
    \item \textbf{Advanced Credit Risk Modeling \& Capital Analytics}  
    \begin{itemize}
        \item Designed, implemented, and monitored Probability of Default (PD), Loss Given Default (LGD), and Capital Planning stress-testing models supporting regulatory, risk appetite, and portfolio management decisions.
        \item Conducted loan-level risk analytics and macro-economic sensitivity analysis, developing scenario frameworks linking GDP, unemployment, interest rates, and sector-specific drivers to credit outcomes.
        \item Led SAS-to-Python model migration in partnership with Technology, productionizing PD/LGD models into the enterprise credit rating platform (Credit Lens) with full documentation, validation, and governance controls.
        \item Owned ongoing performance monitoring for commercial credit models spanning 10+ industries, developing and enhancing back-testing, calibration, and stability diagnostics in SAS and Python; produced statistical and executive-level reports used by Model Risk Management, senior leadership, and external auditors.
    \end{itemize}
    \item \textbf{Cross-Functional Project Leadership \& Innovation}  
    \begin{itemize}
        \item Led cross-functional initiatives across fintech partners, wealth management, credit officers, and model development teams to design and deploy data-driven credit solutions.
        \item Delivered multiple high-impact platforms, including:
         \begin{itemize}
         \item A small-business auto-approval credit model integrating policy rules and statistical risk scoring,
         \item A securities-based lending system combining market risk and credit risk analytics,
         \item Machine-learning–driven early warning systems for proactive credit risk identification.
          \end{itemize}
        \item Translated complex quantitative outputs into actionable insights for senior stakeholders, balancing innovation with regulatory expectations and model governance standards.
    \end{itemize}
    \item \textbf{Diversity, Inclusion \& Organizational Leadership}  
    \begin{itemize}
        \item Co-founded Comerica’s Asian / Pacific Islander Employee Resource Group, recruiting and leading a 15-member leadership team.
        \item Scaled the organization to 400+ active members, organizing firm-wide diversity programming, community outreach, and volunteer initiatives aligned with corporate DEI objectives.
    \end{itemize}
\end{itemize}

\section{Dissertation}

\datedsubsection{\textbf{Did dividend tax policy changes increase Chinese financial market stability?}}{}
\begin{itemize}
    \item \textbf{Objective}: Conduct causal inference/policy evaluations on how dividend tax policies changes affected firms' behavioe and financial markets stability in China using data from 20,000+ firms' financial data in the Chinese stock market.
    \item \textbf{Methods}: Event Study model, Difference-in-Differences model, and Matching Methods (One-to-One Matching, k-Nearest-Neighbor Matching, Propensity Score Matching).
    \item \textbf{Outcomes}: Supported by Tulane SLA Dissertation Fellowship and Laura Bassi Scholarship; Presented findings to economists at top conferences such as the American Economic Association , National Tax Association, Southern Economic Association, Chinese Economists Society annual meetings.
\end{itemize}

%\datedsubsection{\textbf{Impact of health on education and employment: evidence from the NLSY97}}{}
%\textit{Collaborators: Daniela Rivero Bryant, Lu Yao}  
%\begin{itemize}
   % \item \textbf{Objective}: Analyze the relationship between self-reported adolescent health and two key economic outcomes: educational attainment and employment status during early adulthood.
   % \item \textbf{Methods}: Used data from the National Longitudinal Survey of Youth 1997 (NLSY97); Applied Ordinary Least Squares (OLS), Logit models, and Hazard models (survival analysis).
%\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
    \item \textbf{Coding/System}: AWS Sagemaker, Dremio, Stata, R, SAS (\href{https://www.youracclaim.com/badges/c4bce10e-7398-4203-9d11-f9c6723749a4/linked_in_profile}{SAS Certified Advanced Programmer}), SQL, Python, EViews, Markdown, $L^{A}T_{E}X$.
    \item \textbf{Experience with}: Causal Inference, A/B testing, Time-series (ARIMA/GARCH), Machine Learning, Financial Datasets (CRSP, CapIQ, Bloomberg Terminal), Oracle Hyperion, Tableau (Basic), Research on investment/asset pricing, Credit risk modeling, Microsoft Office Suite, Healthcare Datasets (IPUMS, NLSY, CDC database).
\end{itemize}

\end{document}
